Clustering exploration for `r params$sample_id`

### 2024-09-10 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

here we will calculate a TP53 score using AddMduleScore and the genes of the HALLMARK_P53_PATHWAY gene set.

@@

here we will calculate a DNA_repair score using AddMduleScore and the genes of the HALLMARK_DNA_REPAIR gene set.

>>>>

here we will calculate a TP53 score using `AddModuleScore` and the genes of the HALLMARK_P53_PATHWAY gene set.

@@

here we will calculate a DNA_repair score using `AddModuleScore` and the genes of the HALLMARK_DNA_REPAIR gene set.
